curatedMetagenomicData

### 2020-01-27 manuscript_NS_MRD.Rmd
updated

# This calcualtes the group PERMANOVA perma_d(p.low,p.high,"TESTHigh_vesus_Low")
perma_d <- function(x,y,title_text) { # x & y must be either p.low,p.med or p.high
  # Convert to compositional data perma_d(p.low,p.high,"final_highVlow")
  pseqLvH <- merge_phyloseq(x,y) # pseqLvH <- merge_phyloseq(p.low,p.high)
  pseq.rel <- microbiome::transform(pseqLvH, "compositional")
  otu <- abundances(pseq.rel)
  meta <- meta(pseq.rel)
  permanova <- adonis(t(otu) ~ mnd,
               data = meta, permutations=999, method = "bray")
 # P-value
  print(as.data.frame(permanova$aov.tab)["mnd", "Pr(>F)"])  
  dist <- vegdist(t(otu))
  anov <- anova(betadisper(dist, meta$mnd))
  summary(anov)
  tidy(anov)
  coef <- coefficients(permanova)["mnd1",]
  top.coef <- coef[rev(order(abs(coef)))[1:20]]
  par(mar = c(12, 30, 2, 1))
  #KEEP THIS  TO ENSURE THERE IS NOT A MISTAKE IN THE REORDERING BELOW
  #temp <- TeX("Top Genus")
  #png(paste("PERMOVA_",title_text,".png", sep = "" ), width = 450, height = 210,  units     = "mm",
  #res       = 1500)
  #barplot(sort(top.coef), col = rainbow(20), horiz = T, las = 1, main = temp)
  #dev.off() 
  temp <- as.data.frame(top.coef)
  temp$label <- rownames(temp) 
  temp$label <- sub("s_*", "", temp[,2])
  #temp$colour <- ifelse(temp$top.coef < 0, "firebrick1","steelblue")
  p <<- ggplot(temp,aes(reorder(label, top.coef),top.coef,fill = top.coef > 0)) + geom_col(show.legend = FALSE,) + coord_flip() +  xlab('Taxa') + ylab('p value')  + theme_minimal(base_size = 12)  + annotate("text", x = 2.5, y = 0.01, label = "Harmful Taxa") + annotate("text", x = 19, y = -0.01, label = "Beneficial Taxa") + scale_fill_discrete(name = "Taxa") + theme(axis.text.y = element_text(face="italic")) + theme_void()
  save_plot(paste("PERMANOVA_",title_text,".png", sep = "" ), p)
  #ggsave("test_permanova.png", device = "png",width = 297, height = 210, units = "mm")
 }

@@

pseq.subset <- subset_samples(pseq.c, !is.na(mnd) & is.na(disease) & disease == "healthy" & age_category != "child" & age_category != "newborn" & age_category != "schoolage" )

@@

my_atlas_table(atlas.pseq)
alpha_d(pseq,"final_RLWT_1")

>>>>

# This calcualtes the group PERMANOVA perma_d(p.low,p.high,"TESTHigh_vesus_Low")
perma_d <- function(x,y,title_text) { # x & y must be either p.low,p.med or p.high
  # Convert to compositional data perma_d(p.low,p.high,"final_highVlow")
  pseqLvH <- merge_phyloseq(x,y) # pseqLvH <- merge_phyloseq(p.low,p.high)
  pseq.rel <- microbiome::transform(pseqLvH, "compositional")
  otu <- abundances(pseq.rel)
  meta <- meta(pseq.rel)
  permanova <- adonis(t(otu) ~ mnd,
               data = meta, permutations=999, method = "bray")
 # P-value
  print(as.data.frame(permanova$aov.tab)["mnd", "Pr(>F)"])  
  dist <- vegdist(t(otu))
  anov <- anova(betadisper(dist, meta$mnd))
  summary(anov)
  tidy(anov)
  coef <- coefficients(permanova)["mnd1",]
  top.coef <- coef[rev(order(abs(coef)))[1:20]]
  par(mar = c(12, 30, 2, 1))
  #KEEP THIS  TO ENSURE THERE IS NOT A MISTAKE IN THE REORDERING BELOW
  #temp <- TeX("Top Genus")
  #png(paste("PERMOVA_",title_text,".png", sep = "" ), width = 450, height = 210,  units     = "mm",
  #res       = 1500)
  #barplot(sort(top.coef), col = rainbow(20), horiz = T, las = 1, main = temp)
  #dev.off() 
  temp <- as.data.frame(top.coef)
  temp$label <- rownames(temp) 
  temp$label <- sub("s_*", "", temp[,2])
  #temp$colour <- ifelse(temp$top.coef < 0, "firebrick1","steelblue")
  p <<- ggplot(temp,aes(reorder(label, top.coef),top.coef,fill = top.coef > 0)) + geom_col(show.legend = FALSE,) + coord_flip() +  xlab('Taxa') + ylab('p value')  + theme_minimal(base_size = 12)  + annotate("text", x = 2.5, y = 0.01, label = "Harmful Taxa") + annotate("text", x = 19, y = -0.01, label = "Beneficial Taxa") + scale_fill_discrete(name = "Taxa") + theme_classic() + theme(axis.text.y = element_text(face="italic")) 
  save_plot(paste("PERMANOVA_",title_text,".png", sep = "" ), p)
  #ggsave("test_permanova.png", device = "png",width = 297, height = 210, units = "mm")
 }

@@

pseq.subset <- subset_samples(pseq.c, !is.na(mnd) & is.na(disease) | disease == "healthy" & age_category != "child" & age_category != "newborn" & age_category != "schoolage" )

pseq.subset <- subset_samples(pseq.subset, !is.na(nationality) )
atlas.pseq <- subset_samples(atlas.pseq, !is.na(nationality) )

@@

my_atlas_table(atlas.pseq)
alpha_d(pseq.subset,"final_RLWT_1")
